
## <a name="bz"></a> Bugzilla

### <a name="bz_issues"></a> Bugzilla issues

**Download**: [`r file_bz_issues`.gz](../`r url_bz_issues`.gz)

```{r bz_issues}
data <- read.csv(file=url_bz_issues, header=T)
```

File is [``r url_bz_issues``](../`r url_bz_issues`), and has ``r ncol(data)`` columns for ``r nrow(data)`` issues.

### <a name="bz_issues_open"></a> Bugzilla open issues

**Download**: [`r file_bz_issues_open`.gz](../`r url_bz_issues_open`.gz)

```{r bz_issues_open}
data <- read.csv(file=url_bz_issues_open, header=T)
```

File is [``r url_bz_issues_open``](../`r url_bz_issues_open`), and has ``r ncol(data)`` columns for ``r nrow(data)`` issues (all open).

### <a name="bz_evol"></a> Bugzilla evolution

**Download**: [`r file_bz_evol`.gz](../`r url_bz_evol`.gz)

```{r bz_evol}
data <- read.csv(file=url_bz_evol, header=T)
```

File is [``r url_bz_evol``](../`r url_bz_evol`), and has ``r ncol(data)`` columns for ``r nrow(data)`` weeks.

```{r bz_evol_viz}
data.xts <- xts(x = data, order.by = as.POSIXct(data$date))
data.monthly <- apply.monthly(x=data.xts, FUN = nrow)

p <-dygraph(data.monthly[,1],
        main = paste('Monthly issues submissions for ', project_id, sep=''),
        width = "750px", height = 250 ) %>%
      dyRangeSelector()
p
```

### <a name="bz_versions"></a> Versions

**Download**: [`r file_bz_versions`.gz](../`r url_bz_versions`.gz)

```{r bz_versions}
data <- read.csv(file=url_bz_versions, header=T)
```

File is [``r url_bz_versions``](../`r url_bz_versions`), and has ``r ncol(data)`` columns for ``r nrow(data)`` weeks.

```{r bz_versions_viz, echo=FALSE, message=FALSE, results='asis'}
suppressPackageStartupMessages(library(googleVis))
options(gvis.plot.tag='chart')

versions.sorted <- versions[order(versions$Bugs, decreasing = T),]

g <- gvisColumnChart(versions.sorted, options=list(title='List of product versions', legend="{position: 'none'}", width="automatic", height="300px"))
plot(g)
```

### <a name="bz_components"></a> Components

**Download**: [`r file_bz_components`.gz](../`r url_bz_components`.gz)

```{r bz_components}
data <- read.csv(file=url_bz_components, header=T)
```

File is [``r url_bz_components``](../`r url_bz_components`), and has ``r ncol(data)`` columns for ``r nrow(data)`` weeks.

```{r bz_components_viz, echo=FALSE, message=FALSE, results='asis'}
components.sorted <- components[order(components$Bugs, decreasing = T),]

g <- gvisColumnChart(components.sorted, options=list(title='List of product components', legend="{position: 'none'}", width="automatic", height="300px"))
plot(g)
```

